%\begin{table}[h]
    \noindent\begin{longtable}[c]{ p{0.25\textwidth} p{0.25\textwidth} p{0.4\textwidth} }
    \hline
    Word            & English       & Probable etymology  \\
    \hline\endhead
    abaabiã         & hand          &  \\
    ablowa          & old           &  \\
    abrôfô          & white man     & Twi. \textit{borôfo} `white people'  \\
    abuwe           & to fall on the ground%
                                    & Twi \textit{bu} `to fall off`  \\
    adowé           & outsider      & Ndy. \textit{a doo se} `outside \\
    adyamisimidasi  & please        & Ndy. \textit{a de ya mi si mi} ... `it’s here, I see, I'...%
                                      Twi \textit{ndasi} `thank'  \\
    adyasu          & rabbit        &  \\
    adyema          & sickness      &  \\
    afaná           & machete       & Twi \textit{afana} `sword'  \\
    afladu          & friend,%
                      trustworthy person%
                                    &  \\
    afladunuplasi   & haven         &  \\
    aflan           & machete       &  \\
    aflangawo       & bush rum      &  \\
    afofi           & tobacco       &  \\
    afradutongo     & non human speech during spirit possession%
                                    &  \\
    agódu           & drinking calabash%
                                    & Eng. \textit{gourd}  \\
    akema           & drum          & Twi \textit{ôkyerema} `drummer'  \\
    akésua          & egg           & Twi \textit{kosua} `egg'  \\
    akrobi          & child         &  \\
    akrowa          & rice          &  \\
    akukúa          & paddle        &  \\
    amaulî          & tiger         &  \\
    améku           & woman         &  \\
    amékuboi        & daughter, young woman%
                                    &  \\
    amînsu          & ash           & Twi \textit{nso} `ash'  \\
    amintó          & stool         &  \\
    ampuna          & tobacco in a pipe, smoking pipe%
                                    & Twi \textit{abua} `pipe'  \\
    ándo            & young man, age mate%
                                    &  \\
    animbáw         & cemetery      &  \\
    ankama          & axe           &  \\
    atekelebu       & back and forth motion%
                                    &  \\
    atekelebutiki   & paddle        & \textit{-tiki} < Eng. \textit{stick}  \\
    ayêmpẽ          & sharp thing   & Eng. \textit{iron pin}  \\
    ayenkudaí       & jaguar        &  \\
    badyabadya      & quickly       & Twi \textit{bagya} `four footed animal`  \\
    basi            & boss          & Sur. creole  \\
    bifo            & before        & Sur. creole  \\
    bleki           & smoke         &  \\
    blèku           & round         &  \\
    blibla          & foot, leg     &  \\
    bofó            & outsider      & Twi \textit{ôbofo} `destroyer, mischievous person'  \\
    bronsikin       & sun           & Eng. \textit{burn skin}  \\
    bũsũ            & water         & Twi \textit{nsuo} `water'  \\
    bũsuma          & people        & Sur. creole \textit{bun suma} `good people'  \\
    busiman         & a runaway     & Sur. creole \textit{busiman} lit. `forest person'  \\
    danifo          & house         & Twi \textit{ôdani} `house'  \\
    dankagri        & confusion     &  \\
    dasi            & thank         & Twi \textit{ndasi} `thank'  \\
    dômp(l)o        & old, big      & Twi \textit{ôdomfo} `kind person'  \\
    duampõ          & boat          &  \\
    duudru          & forest, night &  \\
    dyaki           & beard         &  \\
    faka            & knife         &  \\
    fang            & very white    & Ndy. \textit{fang} `very white'  \\
    fanga           & receive       & Du. \textit{fangen} `to catch'  \\
    hankaa          & copula ~`to be'%
                                    & Eng. \textit{anchor}  \\
    hantroki        & to smoke      &  \\
    hantuwe         & rifle         & Eng. \textit{hunt}  \\
    hofasi          & how           & Plantation Sranan \textit{hoefasi} `how'  \\
    îniba           & come          & Twi \textit{ba} `come'  \\
    inii            & each          &  \\
    inzii           & iron          & Du. \textit{ijzer} `iron'  \\
    kama            & axe           &  \\
    kangwi          & star          &  \\
    kataki          & heart         &  \\
    kibongola       & sparkle       &  \\
    kobua           & drum          &  \\
    koko            & head          &  \\
    kôkôlo          & hen, rooster  & Twi \textit{okókolo} `rooster'  \\
    kolonton        & African-born slave%
                                    &  \\
    konfo           & priest        &  \\
    kôntôn          & bolster       & Eng. \textit{come strong}  \\
    mamiyé          & to eat        &  \\
    mamsatiki       & reed          & \textit{-tiki} < Eng. \textit{stick}  \\
    manzatiki       & sugar cane    & \textit{-tiki} < Eng. \textit{stick}  \\
    matándu         & egg yolk      &  \\
    matu            & thorn         &  \\
    mintawo         & earth         &  \\
    mlekuboi        & baby          & Eng. \textit{milk boy}  \\
    monti           & nice          &  \\
    montisie        & nicely        &  \\
    naki            & knock         & Sur. creole \textit{naki}, `knock, hit'  \\
    ndama           & hear          & Twi \textit{dam} `to be heard'  \\
    obolowá         & old woman     & Twi \textit{aberewa} `old woman'  \\
    ôbrofô          & white man     & Twi \textit{ôburoni} `white man'  \\
    obutábela       & tobacco       &  \\
    ôkumudya        & evil          &  \\
    ontuô           & gun           & Eng. \textit{hunt}  \\
    osònu           & foot          &  \\
    ôtuwa           & dog           &  \\
    ôyêle           & kaolin        &  \\
    pakwê           & ears          &  \\
    palasi, plasi   & village       &  Du: \textit{plaats} `place'  \\
    pasini          & cassava       &  \\
    pika            & very black    &  \\
    pipli           & person        & Plantation Sranan: \textit{pipli}  \\
    saafuboi        & youngster     & Eng. \textit{soft boy}  \\
    sawa            & wash          &  \\
    sêêmba          & to go         &  \\
    sêpetu          & seed          &  \\
    sêwênu          & seaboat       &  \\
    si              & to see        & Sur. creoles \textit{si} `see'  \\
    sie             & way           & Sur. creoles \textit{fasi} `way'  \\
    singa           & to pull       &  \\
    srampani        & chat          &  \\
    tando           & ancestors     &  \\
    troki           & to sing       &  \\
    yôko            & sick          &  \\
    yóó             & eye           &  \\
    \hline
    %\end{longtable}
    \caption{Kumanti wordlist with potential etymologies.}\label{tab:kumanti}
    \end{longtable}
%\end{table}
